%Original version in April 2002 by Antje Endemann
%
%Adapted for usage in Student Conference course by jubo (050118).
%Optimized for usage with pdflatex. For usage with plain latex,
%figures must be in Postscript (.ps or .eps files) and additional
%packages must be imported.
%Last updated 100105 by jubo
%
%This template works for outline and annotated bibliography
%(deliverable 2) without any changes.
%For usage with full and final papers (deliverables 3 and 4a/b)
%you must make several changes. All necessary changes are
%described in three specific commented sections preceded by
%`%%%%% BEGIN OF ADJUSTMENTS SECTION %%%%%'.
%The changes are in order of appearance:
%   - adjust the `\documentclass' command
%   - uncomment the abstract section
%   - adjust the `\bibliographystyle' command

%%%%% BEGIN OF 1st ADJUSTMENTS SECTION %%%%%
% You must use only one of the following `\documentclass' commands
% For the outline and annotated bibliography (deliverable 2)
% you must use the following command:
%
\documentclass[runningheads,a4paper,oribibl]{llncs}
%
% For the full and final paper (deliverables 3 and 4a/b)
% you must use the command below (and put the one above in comments).
% In other words, the 'oribib' option must be used for Deliverable 2
% but not for 3 and 4a/b.
% 
%
%\documentclass[runningheads,a4paper]{llncs}
%
%%%%% END OF 1st ADJUSTMENTS SECTION %%%%%

\usepackage[T1]{fontenc}  %% needed for special characters (umlaut)
\usepackage[utf8]{inputenc}
\usepackage{graphicx}     %% for graphical things such as including pictures
\usepackage{url}          %% for proper formatting of URLs

\begin{document}

\pagestyle{headings}

\mainmatter

\title{Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations.}

% The abbreviated title will be shown in the headers of even pages.
% You should use the full title unless it is too long.
\titlerunning{Touch Interfaces for Robotic Nozzles in Emergency Situations}

\author{Albin Hübsch}

\institute{
	Department of Computing Science \\
	Umeå University, Sweden \\
	\email{id11ahh@cs.umu.se}
}

\maketitle

%%%%% BEGIN OF 2nd ADJUSTMENTS SECTION %%%%%
% Do NOT include an abstract in the outline and annotated bibliography
% (deliverable 2). For the full and final paper (deliverables 3 and 4a/b),
% you must uncomment the following two commands and place your text for
% the abstract in between them.
%
% \begin{abstract}
%   Here goes the actual text of your abstract.
% \end{abstract}
%
%%%%% END OF 2nd ADJUSTMENTS SECTION %%%%%

\section{Introduction}
Introduction part will contain a purpose of the paper and a motivation for why the paper was made.

\begin{description}
	\item[Purpose] Can a well designed touch interface with differences in color contrast for controlling robotic water cannon nozzles reach a lower level of faulty interactions in emergency situations.
	\item[Motivation] In critical emergency situations, like in the case of fire, a graphical touch user interface should not be the weak link on getting the job done when controlling robotic water cannon nozzles. One wrong push of a touch screen button in the interface can be the difference between life or death.
\end{description}
The main goal with this paper is to evaluate if increased color contrast in a touch screen interface for controlling robotic water cannon nozzles can result in fewer faulty interactions, compared to a low contrast touch interface, in emergency situations. And from this we will present four guidelines on how to design a good touch interface for emergency situations. These guidelines will be useful for anyone designing touch interfaces made for demanding situations.

\section{Method}
In order to be able to test if increased color contrast has an substantial impact on the usability of a touch interface we will design two identical touch interfaces for controlling robotic water cannon nozzles. The only difference between these interfaces will be the color contrast. When designing the touch interface we will follow guidelines defined in the found references. Later these two interfaces will be tested by an A/B test. The test will then be evaluated to produce a result and a conclusion and finally form our four design guidelines.

\subsection{Design of an A/B test}
In order to test if increased color contrast can lower faulty interactions in a touch interface an A/B test will be developed and performed. Two identical applications, despite differences in color contrast, with just a few touch screen buttons will be measured against each other. We will measure both time and amount of errors it takes to perform each given task. The test persons will be told that there is a time limit and they have to do it as fast as they can in order to simulate an emergency situation. Instructions will be given on a secondary screen so that every test is consistent.

\emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.

\subsection{Evaluation of the A/B test}
This section will in short describe the evaluation process of the A/B test. How the test results were collected and what parameters we have had focus on during the test.

\section{Result}
All results produced from the tests are here presented with clear numbers, conclusions and figures/graphics.

\subsection{Evaluation}
The evaluation itself and a text about the evaluation results.

\section{Discussion}
In this section we will discuss the results from the tests. We will discuss what the results mean and how they should and could be interpreted.

\subsection{Conclusions and Guidelines}
Here we will present our conclusions based on the resulting outcome from the tests. We will also present our four guidelines on how to design a touch interface compatible for emergency situations. These guidelines will be created based on the test results.

\subsection{Drawbacks and Limitations}
Present drawbacks and limitations with both the used method and the produced results. Time is limited, therefore a bullet proof test can not be performed which means the results will somewhat be limited in credibility.

\subsection{Future Work}
Due to the limited time we have on this paper there will be a lot of things that can be improved. We will in this section give our suggestions on things that could be done in future or continued work.

%%%%% BEGIN OF 3rd ADJUSTMENTS SECTION %%%%%
% For the outline and annotated bibliography (deliverable 2)
% you must use the following two commands:
%
\nocite{*}  % Includes ALL entries from the .bib-file, even if they are
            % not '\cite{}'-ed in the text above
\bibliographystyle{plain-annote}
%
% For the full and final paper (deliverables 3 and 4a/b)
% use ONLY the following commands (i.e. put the commands above into
% comments and uncomment the command below):
%
% \bibliographystyle{splncs}
%
%%%%% END OF ADJUSTMENTS SECTION %%%%%

\bibliography{Bibliography}

\end{document}
